\documentclass{article}
\include{style}

\begin{document}

    \section*{Bohemian Rhapsody \by Queen}

    \begin{center}
        \begin{enumerate}

            \item[]
            \item[] \intro
            \item Is this the real life?
            \item Is this just fantasy?
            \item Caught in a landslide
            \item No escape from reality
            \item Open your eyes
            \item Look up to the skies and see
            \item I'm just a poor boy, I need no sympathy
            \item Because I'm easy come, easy go
            \item Little high, little low
            \item Any way the wind blows
            \item Doesn't really matter to me, to me

            \item[]
            \item[] \ver{1}
            \item Mama, just killed a man
            \item Put a gun against his head
            \item Pulled my trigger, now he's dead
            \item Mama, life had just begun
            \item But now I've gone and thrown it all away
            \item Mama, ooh
            \item Didn't mean to make you cry
            \item If I'm not back again this time tomorrow
            \item Carry on, carry on as if nothing really matters

            \item[]
            \item[] \ver{2}
            \item Too late, my time has come
            \item Sends shivers down my spine
            \item Body's aching all the time
            \item Goodbye, everybody, I've got to go
            \item Gotta leave you all behind and face the truth
            \item Mama, ooh (Any way the wind blows)
            \item I don't want to die
            \item I sometimes wish I'd never been born at all

            \item[]
            \item[] \instrumental

            \item[]
            \item[] \ver{3}
            \item I see a little silhouetto of a man
            \item Scaramouche, Scaramouche, will you do the Fandango?
            \item Thunderbolt and lightning very, very frightening me
            \item (Galileo) Galileo
            \item (Galileo) Galileo
            \item Galileo Figaro
            \item Magnifico-o-o-o-o
            \item I'm just a poor boy, nobody loves me
            \item He's just a poor boy from a poor family
            \item Spare him his life from this monstrosity
            \item Easy come, easy go, will you let me go?
            \item Bismillah! No, we will not let you go (Let him go!)
            \item Bismillah! We will not let you go (Let him go!)
            \item Bismillah! We will not let you go (Let me go!)
            \item Will not let you go (Let me go!)
            \item Never let you go (Never, never, never, never let me go)
            \item Oh oh oh oh
            \item No, no, no, no, no, no, no
            \item Oh, mama mia, mama mia (Mama mia, let me go)
            \item Beelzebub has a devil put aside for me, for me, for me
            
            \pagebreak

            \item[]
            \item[] \ver{4}
            \item So you think you can stone me and spit in my eye?
            \item So you think you can love me and leave me to die?
            \item Oh, baby, can't do this to me, baby
            \item Just gotta get out, just gotta get right outta here

            \item[]
            \item[] \outro
            \item Ooh, ooh yeah, ooh yeah
            \item Nothing really matters
            \item Anyone can see
            \item Nothing really matters
            \item Nothing really matters to me
            \item Any way the wind blows...

        \end{enumerate}
    \end{center}

\end{document}
