\documentclass{article}
\include{style}


\begin{document}
    
    \section*{High Hopes \of Pink Floyd }

    \begin{center}
        \begin{enumerate}
            \item[] \intro

            \item[] 
            \item[] \verse{1}
            \item Beyond the horizon of the place we lived when we were young;
            \item In a world of magnets and miracles.
            \item Our thoughts strayed constantly and without boundary;
            \item The ringing of the division bell had begun.
            \item Along the Long Road and on down the Causeway;
            \item Do they still meet there by the Cut.
            \item There was a ragged band that followed in our footsteps;
            \item Running before time took our dreams away.
            \item Leaving the myriad small creatures trying to tie us to the ground;
            \item To a life consumed by slow decay.

            \item[]
            \item[] \chorus
            \item The grass was greener;
            \item The light was brighter;
            \item With friends surrounded;
            \item The nights of wonder.
            
            \item[]
            \item[] \verse{2}
            \item Looking beyond the embers of bridges glowing behind us;
            \item To a glimpse of how green it was on the other side.
            \item Steps taken forwards but sleepwalking back again;
            \item Dragged by the force of some inner tide.
            \item At a higher altitude with flag unfurled;
            \item We reached the dizzy heights of that dreamed of world.

            \item[]
            \item[] \instrumental

            \item[]
            \item[] \verse{3}
            \item Encumbered forever by desire and ambition;
            \item There's a hunger still unsatisfied.
            \item Our weary eyes still stray to the horizon;
            \item Though down this road we've been so many times.
            
            \item[]
            \item[] \chorus
            \item The grass was greener;
            \item The light was brighter;
            \item The taste was sweeter;
            \item The nights of wonder;
            \item With friends surrounded;
            \item The dawn mist glowing;
            \item The water flowing;
            \item The endless river;
            \item For ever and ever.

            \item[]
            \item[] \instrumental

            \item[]
            \item[] \outro

            \item "Is that Charlie? Hello Charlie! Great..."

        \end{enumerate}
    \end{center}

\end{document}
